Spin canonical rings of log stacky curves

### 2015-07-14 curves-write-up/spin-cring.tex
edits to idea of proof below monster

\sssec*{Idea of Proof:} To show $\supseteq$, we show that $T \subseteq \initial(I)$, which follows immediately from $(1)$ and $(2)$. Then, we show that $\subseteq$ follows from condition $(3)$ and the fact that no terms in $S$ can be contained in $\initial(I)$ because $(1)$ implies that $S$ is a basis.

@@

\begin{lem}
\label{lem:sat-1}
Let $X$ be a genus $g$ curve and $\halfcan' \in \BQ \otimes \di X$
satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$. Suppose $P$ is not a base-point of $k\halfcan'$ for all $k \in \BN$, meaning we can choose generators $u, x_1, \ldots, x_m$ of $R_{\halfcan'}$ in degree at most $\tau$ for some $\tau\in \BN$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.  Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
for some $\alpha, \beta \in \BN$ such that
\begin{align}
\label{eqn:deg1-sat-ind}
	h^0(X, \lfloor k \halfcan \rfloor) &= h^0(X, \lfloor k \halfcan'
	\rfloor) + \left\lfloor k \frac{\alpha} {\beta} \right \rfloor &&\text{ for all } k \in \mathbb{
	N}.
\end{align}
Let
\[
	0 < \frac{c_1}{k_1} < \ldots < \frac{c_n}{k_n} = \frac{\alpha}{\beta}
\]
be the positive best lower approximations of $\frac{\alpha}{\beta}$
{\rm(}similar to Remark ~\ref{rem:lower-approximation}{\rm)}.
Then,

@@

\item[(c)] Let $\tau = \max(1,
	\max_{1 \leq i \leq m}(\deg(x_i)))$. Then, $R_\halfcan$ is generated over $R_\halfcan'$
	in degrees up to $\beta$ with $I$ generated over $I'$ in
	degrees up to $\max(2 \beta, \beta + \tau).$
\end{enumerate}
\end{lem}

\sssec*{Idea of proof:} The proof will be fairly involved. To show part (a), we first define an set of generators of $R_\halfcan$ over $R_{\halfcan'}$, with one generator corresponding to each best lower approximation. We then use Riemann--Roch to count the dimension of $R_\halfcan$ over $R_{\halfcan'}$, showing that the set of elements we produce forms a basis.

Next, part (b) immediately follows from an application of Lemma ~\ref{lem:relations_from_generators_induction}, we only need verify the hypotheses of Lemma ~\ref{lem:relations_from_generators_induction}. The first two hypotheses follow immediately from the construction of block order. Checking the third condition is quite technical, but the conditions ~\ref{custom:sat-1-*}, ~\ref{custom:sat-1-**}, and ~\ref{custom:sat-1-***} give certain slope conditions, which are precisely what is needed to verify the third condition of Lemma ~\ref{lem:relations_from_generators_induction}.

>>>>

\sssec*{Idea of Proof:} To show $\supseteq$, we show $T \subset \initial(I),$ which follows immediately from $(1)$ and $(2)$. Then, $\subseteq$ follows from condition $(3)$, since $(1)$ implies $S$ is a basis, so no terms in $S$ can be contained in $\initial(I)$.

@@

\begin{lem}
\label{lem:sat-1}
Let $X$ be a genus $g$ curve and $\halfcan' \in \BQ \otimes \di X$
satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$. Suppose $P$ is not a base-point of $k\halfcan'$ for all $k \in \BN$, meaning we can choose generators $u, x_1, \ldots, x_m$ of $R_{\halfcan'}$ in degree at most $\tau$ for some $\tau\in \BN$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.  Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
for some $\alpha, \beta \in \BN$ such that
\begin{align}
\label{eqn:deg1-sat-ind}
	h^0(X, \lfloor k \halfcan \rfloor) &= h^0(X, \lfloor k \halfcan'
	\rfloor) + \left\lfloor k \frac{\alpha} {\beta} \right \rfloor &&\text{ for all } k \in \mathbb{
	N}.
\end{align}
Let
\[
	0 < \frac{c_1}{k_1} < \ldots < \frac{c_n}{k_n} = \frac{\alpha}{\beta}
\]
be the positive best lower approximations of $\frac{\alpha}{\beta}$
(similar to Remark ~\ref{rem:lower-approximation}).
Then,

@@

\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$
	in degrees at most $\beta$ with $I$ generated over $I'$ in
	degrees at most $\max(2 \beta, \beta + \tau)$ (where $\tau = \max(1,
	\max_{1 \leq i \leq m}(\deg(x_i)))$).
\end{enumerate}
\end{lem}

\sssec*{Idea of proof:} The proof will be fairly involved. To show part (a), we first define an set of generators of $R_\halfcan$ over $R_{\halfcan'}$, with one generator corresponding to each positive best lower approximation of $\frac{\alpha}{\beta}$. We then use Riemann--Roch to count the dimension of $R_\halfcan$ over $R_{\halfcan'}$, showing that the set of elements we produce forms a basis.

Next, part (b) immediately follows from the conclusion of Lemma ~\ref{lem:relations_from_generators_induction}, so we only need verify the hypotheses of that lemma. The first two hypotheses follow immediately from the construction of block order. Checking the third condition is quite technical, but the conditions ~\ref{custom:sat-1-*}, ~\ref{custom:sat-1-**}, and ~\ref{custom:sat-1-***} give certain slope conditions, which are precisely what is needed to verify the third condition of Lemma ~\ref{lem:relations_from_generators_induction}.
